Expert-In-The-Loop Causal Discovery: Integrating Expert Knowledge

### 2024-08-05 paper/main.tex
Updates

Using this mixed data partial association measure, we propose a method to rank
CI tests, and use it for model construction and modification. Given a
potentially empty DAG $ G $ and a dataset $ D $, for each pair for variable $ X
$ and $ Y $ in $ G $:
\begin{itemize}
	\item If there is no edge between $ X $ and $ Y $, we compute p-value for the CI test $ X \ci Y \rvert pa_G(X) \cup pa_G(Y) $ and the partial association measure: $ \rho(X, Y; pa_G(X) \cup pa_G(Y)) $.
	\item If there is an edge between $ X $ and $ Y $, we compute p-value for the CI test $ X \ci Y \rvert pa_\underling{G}(X) \cup pa_{\underline{G}(Y)} $ and the partial association measure: $ \rho(X, Y; pa_{\underline{G}}(X) \cup pa_{\underline{G}}(Y) $.
\end{itemize}

>>>>

Using this mixed data partial association measure, we propose a method to rank
CI tests, and use it for model construction and modification. Given a
potentially empty DAG $ G $ and a dataset $ D $, for each pair for variable $ X
$ and $ Y $ in $ G $:
\begin{itemize}
	\item If there is no edge between $ X $ and $ Y $, we compute p-value for the CI test $ X \ci Y \rvert pa_G(X) \cup pa_G(Y) $ and the partial association measure: $ \rho(X, Y; pa_G(X) \cup pa_G(Y)) $.
	\item If there is an edge between $ X $ and $ Y $, we compute p-value for the CI test $ X \ci Y \rvert pa_{\underline{G}}(X) \cup pa_{\underline{G}}(Y) $ and the partial association measure: $ \rho(X, Y; pa_{\underline{G}}(X) \cup pa_{\underline{G}}(Y) $.
\end{itemize}
